---
title: "挪威养老基金"
subtitle: "Norway The Government Pension Fund Global"
author: "Tony D"
date: "2025-04-24"

categories: 
  - AI
  - R
  - Python

  
execute:
  warning: false
  error: false
  eval: false
  

image: 'images/logo.svg'

#draft: true
---

An overview of Norway's Government Pension Fund Global, including its purpose and links to resources.

This document provides an overview of the Government Pension Fund Global of Norway, one of the world's largest sovereign wealth funds. It explains the fund's purpose, which is to manage the financial reserves from Norway's oil and gas resources for the benefit of current and future generations. The document also includes links to the fund's official website, investment data, and a related podcast, offering a comprehensive resource for those interested in learning more about this significant financial institution.

The Government Pension Fund Global was established after Norway discovered oil in the North Sea. 

The fund was set up to shield the economy from ups and downs in oil revenue. It also serves as a financial reserve and as a long-term savings plan so that both current and future generations of Norway get to benefit from our oil wealth.


https://www.nbim.no/en



```{r}
library(ellmer)
library(tidyverse)
library(srt)
library(openxlsx)
library(readxl)
library(lares)
library(tuneR)
library(stringr)
library(rvest)
library(av)
```

# podcast


https://shows.acast.com/in-good-company-with-nicolai-tangen


```{r}
one_podcast='https://shows.acast.com/in-good-company-with-nicolai-tangen/episodes/highlights-debra-crew-ceo-of-diageo'

audio_page <- read_html(one_podcast)
    
# 提取音频标题，property="og:title"的meta元素的content值
title <- audio_page %>%
html_nodes('meta[property="og:title"]') %>%
html_attr("content")

title  

# 提取音频下载链接，property="og:audio"的meta元素的content值
audio_url <- audio_page %>%
  html_nodes('meta[property="og:audio"]') %>%
  html_attr("content")

audio_url
```

```{r}
output_file_name=paste0(title,".mp3")
download.file(url = audio_url, destfile = output_file_name)
```


# data


https://www.nbim.no/en/investments/all-investments/#/


# video

https://www.youtube.com/watch?v=mT6mRJehJdw


